---
title: "Are your employees burning out?"
author: "Amy Yang"
date: "17/10/2021"
output:
  html_document:
    number_sections: no
    fig_caption: yes
    toc: yes
    toc_depth: '2'
  word_document:
    number_sections: no
    fig_caption: yes
    toc: yes
    toc_depth: '2'
  pdf_document:
    number_sections: no
    fig_caption: yes
    toc: yes
    toc_depth: '2'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This R Markdown file is to demonstrate the idea of Adjustment using the dataset of employee burnout rate from [Kaggle](https://www.kaggle.com/blurredmachine/are-your-employees-burning-out). As explained by Brian in [Regression Models for Data Science in R](https://leanpub.com/regmods/read#leanpub-auto-adjustment), adjustment describes how the third variable impacts the relationship between another two in a linear model. 

## Data Tidying and Visualisation

```{r, message=FALSE, warning=FALSE}
# Load library
library(tidyverse)
library(corrplot)
library(janitor)

```

```{r, message=FALSE, warning=FALSE}
# Import csv file
e_burnout <- read_csv("employee_burn_out_rate.csv")


```

```{r, message=FALSE, warning=FALSE}
# Clean and view the column names
e_burnout <-clean_names(e_burnout)
names(e_burnout)

```


```{r, message=FALSE, warning=FALSE}
# View the data structure
glimpse(e_burnout)

```

There are 9 variables in the dataset including both categorical and numerical variables. Some variables are clarified as below.

-  Gender: Male or Female
-  Company Type: Service or Product
-  WFH Setup Available: Yes or No
-  Designation: The designation of the employee of work in the organization with range of [0.0, 5.0]. Bigger value refers to higher designation.
-  Resource Allocation: The amount of resource allocated to employees to work, for example working hours, with range of [1.0, 10.0]. Higher value means more resources.
-  Mental Fatigue Score: The level of fatigue mentally employees is facing, with range of [0.0, 10.0], where 0.0 means no fatigue and 10.0 means completely fatigue.
-  Burn Rate: the rate of burnout while working with range of [0.0, 10.0]. Higher value means more burnout. 


```{r, message=FALSE, warning=FALSE}
# convert the data format to date
e_burnout$date_of_joining <- as.Date(e_burnout$date_of_joining,"%d/%m/%Y")

```


```{r, message=FALSE, warning=FALSE}
# Check missing values and drop rows with na
cbind(
  lapply(
    lapply(e_burnout, is.na),sum)
)
e_burnout_clean <- drop_na(e_burnout)

```

To visualise the correlation matrix with `corrplot()`, the following categorical variables were assigned to be 0 or 1.

-  Gender: Female is 1 and Male is 0
-  Company Type: Service is 1 and Product is 0
-  WFH Setup Available: Yes is 1 and No is 0

Also, the variable *countdays* was calculated as the time period (days) between today's date and employee's joining date. 

```{r, message=FALSE, warning=FALSE}

# Transform the categorical variables and date variable
e_burnout_num <- 
  e_burnout_clean %>% 
  mutate(
        countdays=as.numeric(as.difftime(Sys.Date()-date_of_joining)),
        isfemale=ifelse(gender=="Female",1,0),
        isservice=ifelse(company_type=="Service",1,0),
        iswfh=ifelse(wfh_setup_available=="Yes",1,0)
         )
glimpse(e_burnout_num)

```

```{r, message=FALSE, warning=FALSE}

# Correlation matrix with corrplot
e_burnout_sub <- 
  e_burnout_num %>% 
  select(isfemale,isservice,iswfh,countdays,designation,resource_allocation,mental_fatigue_score,burn_rate)
corr_burnout <- cor(e_burnout_sub)
corrplot(corr_burnout, type = "upper", tl.col = "darkblue", tl.srt = 45,
         addCoef.col = "darkorange")

```

It was found from the correlation matrix, employee burnout rate was strongly associated with the level of mental fatigue, allocated resources and the designation within the organisation. Among the remaining 4 variables, the availability for work from home setup had the greatest impact on reducing the burnout for employees.

## Adjustment

First, a linear regression model was built to explain the burnout rate with the variable work from home(wfh) setup availability. As shown in the summary below, wfh setup availability was highly significant with a p-value less than 0.001. 

```{r}
# Model with wfh setup availability
lm_w <- lm(burn_rate ~ iswfh, data = e_burnout_num)
summary(lm_w)

```

We then added the regressor Mental fatigue score into the model and looked at its impact on the relationship between wfh set availability and employee burnout rate.

```{r}
# Model with mental fatigue score
lm_m <- lm(burn_rate ~ mental_fatigue_score, data = e_burnout_num)
summary(lm_m)

# Model with mental fatigue score and wfh setup availability
lm_mw <- lm(burn_rate ~ mental_fatigue_score+iswfh, data = e_burnout_num)
summary(lm_mw)

# Visualise the adjustment by adding the variable mental fatigue score
e_burnout_wfh <- e_burnout_num %>% filter(iswfh==1)
e_burnout_notwfh <- e_burnout_num %>% filter(iswfh==0)
ggplot(e_burnout_num,aes(mental_fatigue_score,burn_rate))+
  geom_point(aes(color=wfh_setup_available))+
  geom_hline(yintercept = mean(e_burnout_wfh$burn_rate), color = "aquamarine2", lwd = 1, lty = 2) +
  geom_hline(yintercept = mean(e_burnout_notwfh$burn_rate), color = "pink", lwd = 1, lty = 2)+
  geom_abline(intercept = coef(lm_mw)[1]+coef(lm_mw)[3], slope = coef(lm_mw)[2], color = "aquamarine2", lwd = 1.5) +
  geom_abline(intercept = coef(lm_mw)[1], slope = coef(lm_mw)[2], color = "pink", lwd = 1.5) +
  geom_abline(intercept = coef(lm_m)[1], slope = coef(lm_m)[2])+
  labs(x="Mental fatigue score",y="Employee burnout rate",color="WFH setup available")+
  theme_bw()

```

This plot revealed that the variable Mental fatigue score was closely related to whether the wfh facility was available for employees. The Mental fatigue score was more likely to be higher when wfh setup was not available. This is similar to Experiment 2 discussed in [Regression Models](https://leanpub.com/regmods/read#leanpub-auto-adjustment) although in our case there was some vertical overlap between the red and green points. If the variable Mental fatigue score was disregarded, employees without wfh setup availability had noticeably higher burnout rate compared to the counterparts with wfh facility. However, if we accounted for the variable Mental fatigue score, the difference in burnout rate between these two groups was almost gone. The effect of wfh setup availability on burnout rate was largely explained by the Mental fatigue score. This could also be seen from the result of model lm_m showing 89.19% variability of burnout rate was explained by the model.

Using the same approach, we explored the impact on the relationship between wfh setup availability and burnout rate by adding the variable Resource allocation and Designation respectively into the model.

```{r}
# Model with resource allocation
lm_r <- lm(burn_rate ~ resource_allocation, data = e_burnout_num)
summary(lm_r)

# Model with resource allocation and wfh setup availability
lm_rw <- lm(burn_rate ~ resource_allocation+iswfh, data = e_burnout_num)
summary(lm_rw)

# Visualise the adjustment by adding the variable resource allocation
ggplot(e_burnout_num,aes(resource_allocation,burn_rate))+
  geom_point(aes(color=wfh_setup_available))+
  geom_hline(yintercept = mean(e_burnout_wfh$burn_rate), color = "aquamarine2", lwd = 1, lty = 2) +
  geom_hline(yintercept = mean(e_burnout_notwfh$burn_rate), color = "pink", lwd = 1, lty = 2)+
  geom_abline(intercept = coef(lm_rw)[1]+coef(lm_rw)[3], slope = coef(lm_rw)[2], color = "aquamarine2", lwd = 1.5) +
  geom_abline(intercept = coef(lm_rw)[1], slope = coef(lm_rw)[2], color = "pink", lwd = 1.5) +
  geom_abline(intercept = coef(lm_r)[1], slope = coef(lm_r)[2])+
  labs(x="Resource allocation",y="Employee burnout rate",color="WFH setup available")+
  theme_bw()

```


```{r}
#Model with designation
lm_d <- lm(burn_rate ~ designation, data = e_burnout_num)
summary(lm_d)

# Model with designation and wfh setup availability
lm_dw <- lm(burn_rate ~ designation+iswfh, data = e_burnout_num)
summary(lm_dw)

# Visualise the adjustment by adding the variable designation
ggplot(e_burnout_num,aes(designation,burn_rate))+
  geom_point(aes(color=wfh_setup_available))+
  geom_hline(yintercept = mean(e_burnout_wfh$burn_rate), color = "aquamarine2", lwd = 1, lty = 2) +
  geom_hline(yintercept = mean(e_burnout_notwfh$burn_rate), color = "pink", lwd = 1, lty = 2)+
  geom_abline(intercept = coef(lm_dw)[1]+coef(lm_dw)[3], slope = coef(lm_dw)[2], color = "aquamarine2", lwd = 1.5) +
  geom_abline(intercept = coef(lm_dw)[1], slope = coef(lm_dw)[2], color = "pink", lwd = 1.5) +
  geom_abline(intercept = coef(lm_d)[1], slope = coef(lm_d)[2])+
  labs(x="Designation",y="Employee burnout rate",color="WFH setup available")+
  theme_bw()

```

Looking at the plots above,the marginal(ignoring Resource allocation/Designation) and conditional (using Resource allocation/Designation) associations differ. This finding is similar to what we discovered by adding the variable Mental fatigue score. When Resource allocation/Designation was ignored, the marginal mean for burnout rate of the group without wfh facility was around 0.12 higher over the group with wfh facility. However,the difference in intercept between these two groups was narrowed down to 0.027 and 0.057 respectively when Resource allocation 
or Designation was accounted into the model.


## Conclusion

The idea of Adjustment helps us understand the effect on the relationship between a predictor and response when other variables are accounted for in multivariable regression analysis. This R Markdown used the dataset of employee burnout rate and illustrated how the relationship between the work from home setup availability and employee burnout rate was impacted by the additional variables Mental fatigue score, Resource allocation and Designation separately. 

